experiment 1

### 2021-11-11 experiments/experiment 1/experiment-1.Rmd
Comparison with main branch

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

@@

knitr::opts_knit$set(progress = TRUE, verbose = FALSE, cache = TRUE)

@@

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- TRUE
```

@@

```{r eval = eval_dynamics_flag}
sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[max_diversty_all]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

@@

```{r eval = FALSE}
visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
```

@@

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
saveRDS(parameter, here("experiments/experiment 1/data/TEST_parameter.RDS"))
saveRDS(var_expt, here("experiments/experiment 1/data/TEST_var_expt.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
parameter <- readRDS(here("experiments/experiment 1/data/TEST_parameter.RDS"))
var_expt <- readRDS(here("experiments/experiment 1/data/TEST_var_expt.RDS"))

var_expt_res <- run_ss_var_experiment(parameter, var_expt)

saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 80'000, 20 x 20 factorial, reference maximum diversity
readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
  mutate(sim_length = 80000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
# var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
#   mutate(sim_length = 1000000)
# # stab_data2 <- var_expt2 %>%
# #   group_by(CB_var_gmax_s, CB_var_h_s,
# #            SB_var_gmax_s, SB_var_h_s,
# #            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
# #   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data2 <- var_expt2 %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res)))
# stab_data2 <- unnest(stab_data2, cols = c(stability_measures))
# saveRDS(stab_data2, here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
# var_expt3 <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data3 <- var_expt3 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data3 <- unnest(stab_data3, cols = c(stability_measures))
# saveRDS(stab_data3, here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# var_expt4 <- readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000)
# stab_data4 <- var_expt4 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data4 <- unnest(stab_data4, cols = c(stability_measures))
# saveRDS(stab_data4, here("experiments/experiment 1/data/stab_data_300000.RDS"))
readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
  mutate(sim_length = 300000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
# var_expt5 <- readRDS(here("experiments/experiment 1/data/stab_data_300000.RDS")) %>%
#   mutate(sim_length = 1000000)
# stab_data5 <- var_expt5 %>%
#   group_by(CB_var_gmax_s, CB_var_h_s,
#            SB_var_gmax_s, SB_var_h_s,
#            PB_var_gmax_s, PB_var_h_s, sim_length) %>%
#   do(stability_measures = get_stability_measures(.$ss_res[[1]]))
# stab_data5 <- unnest(stab_data5, cols = c(stability_measures))
# saveRDS(stab_data5, here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

## SS, no diversity, all diversity, CB only, and SBPB only

```{r}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))

@@

@@

@@

@@

## Look at stability measures

### Calculations
```{r}
stab_data <- bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
)

@@

### Plot raw
```{r}

@@

### Plot log
```{r}

@@

## Extra SBPB diversity

```{r}
var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

@@

### raw
```{r}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

### log
```{r}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

all_stab_results<- all_stab_results %>%
    mutate(var_treat = forcats::fct_relevel(var_treat, levels = c("CB", "SB-PB", "CB-SB-PB")))

@@

## What effect of changing the length of the simulations

```{r}
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))

@@

# Some puzzles

@@

```{r}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r eval = eval_dynamics_flag}
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
```

```{r}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = FALSE}
a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
initial_CBs <- 1#10^seq(0, 0, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)
var_expt_master <- var_expt
var_expt <- var_expt_master[381,]
```

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
```

```{r}
library(here)
zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))

@@

```{r eval = FALSE}
var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

@@

```{r echo = FALSE}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

@@

With the CB diversity multiplier set at `r CB_var_multiplier` and the SB/PB multiplier set at `r SBPB_var_multiplier` the range of realised growth rates of CB is `r CB_gr_range`, range of SB is `r SB_gr_range`, and range of PB is `r PB_gr_range`.

>>>>

---
title: "experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

knitr::opts_knit$set(
  progress = TRUE, 
  verbose = FALSE, 
  cache = TRUE
)

@@

library(microxanoxBeta)
if (packageVersion("microxanoxBeta") < package_version("0.2.3")) {
  stop("microxanox version needs to be at least 0.2.3!")
}
library(tidyverse)
library(patchwork)
library(here)
source(here("R/various_useful_functions.r"))
zero <- 0 ## don't change
unity <- 1 ## don't change!!!
options(mc.cores = 7)
eval_dynamics_flag <- FALSE
```

@@

### Medium diversity

```{r eval = eval_dynamics_flag}
try_me <- 311
sim_number2 <- num_div_treatment_levels
parameter$strain_parameter <- var_expt$pars[[try_me]]
parameter$strain_parameter$initial_state <- sim_res_novar3$strain_parameter$initial_state
sim_res_highvar3 <- run_simulation(parameter)
saveRDS(sim_res_highvar3, here("experiments/experiment 1/data/sim_res_highvar3.RDS"))
```

@@

```{r eval = FALSE, echo = FALSE}
visualise_temporal_env_eco(sim_res_novar3, sim_res_highvar3)
```

@@

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 1000000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 1000000,
  sim_sample_interval = 1000000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)
saveRDS(parameter, here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS"))
saveRDS(var_expt, here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))
```

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/experiment 1/data/parameter_1e6_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/experiment 1/data/var_expt_1e6_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS"))
```

@@

## sim length 80'000, 20 x 20 factorial, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS")) %>%
#   mutate(sim_length = 80000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))

## sim length 1'000'000, 20 x 20 factorial, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS")) %>%
#   mutate(sim_length = 1000000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 5x maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS")) %>%
#   mutate(sim_length = 1000000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

## sim length 300'000, 20 SBPBgrad, reference maximum diversity
# readRDS(here("experiments/experiment 1/data/ss_data_300000_small.RDS")) %>%
#   mutate(sim_length = 300000) %>% 
#   multidplyr::partition(cluster) %>%
#   mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
#   collect() %>%
#   unnest(cols = c(stability_measures)) %>%
#   saveRDS(here("experiments/experiment 1/data/stab_data_300000.RDS"))

## sim length 1'000'000, 20 SBPBgrad, 2xCB variation, 6xSBPB variation
readRDS(here("experiments/experiment 1/data/ss_data_1e6_x2x6_factorial.RDS")) %>%
  mutate(sim_length = 1000000) %>% 
  multidplyr::partition(cluster) %>%
  mutate(stability_measures = list(get_stability_measures(ss_res))) %>%
  collect() %>%
  unnest(cols = c(stability_measures)) %>%
  saveRDS(here("experiments/experiment 1/data/stab_data_1e6_x2x6_factorial.RDS"))
```

## SS, no diversity, all diversity, CB only, and SBPB only
No Experimental data

```{r, eval = FALSE, echo = FALSE}
## find various combinations of diversity
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))

@@

```{r, eval = FALSE, echo = FALSE}

@@

```{r, eval = FALSE, echo = FALSE}
p_overlay1 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_diversty_all,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay1
```

```{r, eval = FALSE, echo = FALSE}
p_overlay2 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_CB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay2

@@

```{r, eval = FALSE, echo = FALSE}
p_overlay3 <- plot_ss_result2(var_expt[no_diversity,]$ss_res[[1]],
                             var_expt[max_only_SBPB_diversity,]$ss_res[[1]],
                             xlims = c(-7, -1))
p_overlay3

@@

## Look at stability measures
No experimental data.

### Calculations
```{r, eval = FALSE, echo = FALSE}
stab_data <- bind_rows(
  readRDS(here("experiments/experiment 1/data/stab_data_1000000_20factorial.RDS")), 
  readRDS(here("experiments/experiment 1/data/stab_data_80000.RDS"))
)

@@

### Plot raw
```{r, eval = FALSE, echo = FALSE}

@@

### Plot log
```{r, eval = FALSE, echo = FALSE}

@@

## Extra SBPB diversity
No experimental data.

```{r, eval = FALSE, echo = FALSE}
var_expt_x <- readRDS(here("experiments/experiment 1/data/ss_data_1e6_noCB_5xSBPB_.RDS"))
stab_data_x <- readRDS(here("experiments/experiment 1/data/stab_data_1e6_noCB_5xSBPB_.RDS"))

@@

### raw
```{r, eval = FALSE, echo = FALSE}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_raw)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

### log
```{r, eval = FALSE, echo = FALSE}
stab_data_x %>%
  filter(Species == "O") %>%
  ggplot(aes(x = SB_var_gmax_s, y = hyst_range_log)) +
  geom_point() +
  xlab("Amount of trait variation\n[see text for units]") +
  ylab("Extent of bistability region\n[log10 oxygen diffusivity]") +
  labs(col = "Variation in\nonly these\nfunctional groups")
##ggsave("manuscript/figures/extent_of_bistab1.pdf", height = 4)

@@

@@

## What effect of changing the length of the simulations
No Experimental data.

```{r, eval = FALSE, echo = FALSE}
var_expt1 <- readRDS(here("experiments/experiment 1/data/ss_data_1000000_20factorial.RDS"))
var_expt2 <- readRDS(here("experiments/experiment 1/data/ss_data_80000.RDS"))

@@

# FROM HERE NOT CHANGED TO NEW FORMAT!!!!!!
# Some puzzles

@@

```{r, eval = FALSE, echo = FALSE}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r eval = FALSE, echo = FALSE}
sim_res_novar1 <- run_simulation(parameter_values = var_expt$pars[[max_only_SBPB_diversity]],
                          initial_state = initial_state)
saveRDS(sim_res_novar1, here("experiments/experiment 1/data/puzzle1_2.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
sim_res_novar1 <- readRDS(here("experiments/experiment 1/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

@@

```{r eval = FALSE, echo = FALSE}
a_Os <- 10^seq(-2.479, -2.4785, length=grid_num_a) ## sequence of a_0 values
initial_CBs <- 1#10^seq(0, 0, length=grid_num_N) ## sequence of N values
initial_PBs <- 1e8 ## not varied
initial_SBs <- 1e8 ## not varied
# next line creates all possible combinations
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)
var_expt_master <- var_expt
var_expt <- var_expt_master[381,]
```

```{r, eval = FALSE, echo = FALSE}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_zoom.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
library(here)
zoom <- readRDS(here("experiments/experiment 1/data/ss_data_zoom.RDS"))

@@

```{r eval = FALSE, echo = FALSE}
var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

@@

```{r echo = FALSE, eval = FALSE}
num_CB_strains <- 9
num_SB_strains <- 9
num_PB_strains <- 9

@@

<!-- With the CB diversity multiplier set at ` CB_var_multiplier` and the SB/PB multiplier set at ` SBPB_var_multiplier` the range of realised growth rates of CB is ` CB_gr_range`, range of SB is ` SB_gr_range`, and range of PB is ` PB_gr_range`. -->
